Use Of Jigsaw Puzzle Solving Algorithms In The Real World

### 2023-11-22 LaTeX_paper/paper.tex
fix abstract
Add introduction

\section{Abstract}
This paper examines the Jigsaw puzzle problem,
which has already been extensively studied in the literature.
Several algorithms with efficient time complexity have been developed
specifically for ``digital''~\ref{fig:figure_digital_puzzle} jigsaw puzzles. However, the counterpart:
the ``real world' jigsaw puzzle, has received relatively little attention
in the literature. While some small-scale projects have addressed this issue,
we were unable to find any papers discussing it.

@@

\section{Introduction}
\subsection{Classification}
This paper will focus on Type 2 puzzles. A Type 2 puzzle is one where the position and orientation of each piece are unknown.
\subsection{Digital vs Real-World Jigsaw Puzzles}

>>>>

\begin{abstract}
This paper examines the Jigsaw puzzle problem,
which has already been extensively studied in the literature.
Several algorithms with efficient time complexity have been developed
specifically for ``digital''~\ref{fig:figure_digital_puzzle} jigsaw puzzles. However, the counterpart:
the ``real world' jigsaw puzzle, has received relatively little attention
in the literature. While some small-scale projects have addressed this issue,
we were unable to find any papers discussing it.

@@

\end{abstract}

\section{Introduction}
It is fair to say that we are all familiar with jigsaw puzzles.
Understanding the ``rules'' necessary to solve a puzzle is
extremely easy, but actually solving large-sized puzzles
is not an easy task, neither for humans nor for computers.

While the problem may appear to be a futile style exercise,
it could have concrete applications in the future. For instance,
it could be applied to the reconstruction of archaeological finds,
such as a terracotta pot~\ref{fig:pot}.

% figure of real jigsaw puzzle    
\begin{figure}[h]
  \caption{A practical application of a jigsaw puzzle}~\label{fig:pot}
  \includegraphics[height=0.25\textwidth]{pictures/terracotta_pot.jpg}
  \centering
\end{figure}

\subsection{context}
\subsubsection{Classification}
This paper will focus on Type 2 puzzles. A Type 2 puzzle is one where the position and orientation of each piece are unknown.
\subsection{Digital vs Real-World Jigsaw Puzzles}
